Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-04-13 KY-4.14.tex
update

We observe that either higher density (F$\rightarrow$C$\rightarrow$E)\
or higher velocity (G$\rightarrow$C$\rightarrow$A) of the source\
can enhance the intensity of the shocks driven into the atmosphere,\
and makes the post-shock region hotter,\
as well as leads the bubbles to be more asymmetric about the GC.
This is because the denser/faster jets are more likely to\
break through the thin disk in a short time, resulting in\
the jets have inadequate time to interact with the disk to change its orientations,
and therefore more difficult to be vertically elongated by stratified atmosphere.
{\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?}
{\color{blue} PH: Thanks! I have added this point to the text above.}

{\color{red} KY: The meaning of this sentence is a bit unclear. You mean changing the source density and changing the velocity will give similar results, right?}
{\color{blue} PH: I have deleted the unclear sentence since I feel it is pointless.}

Finally, we find that increasing the source temperature (B$\rightarrow$C$\rightarrow$D)\
not only improves the symmetry of the bubbles but also increases the temperature
inside the bubbles at the present time. This result implies that a high-temperature source
helps the jets ablate the clumpy dense gas away and pours into the atmosphere
through the intercloud channels of the clumpy disk. In contrast,
if source temperature is not high enough,
the jets cannot effectively ablate the high-density cloud within 12.39 Myr,
resulting in the formation of asymmetrical bubbles (the run B).

{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?}
{\color{blue} PH: Yes. To make the difference more obvious,
I have expanded the temperature range by a factor of 5. i.e. $T_{D}/T_{C}=T_{C}/T_{B}\sim50$.}

>>>>

We observe that either higher density (F$\rightarrow$C$\rightarrow$E)\
or higher velocity (G$\rightarrow$C$\rightarrow$A) of the source\
can enhance the intensity of the shocks driven into the atmosphere,\
and makes the post-shock region hotter,\
as well as leads the bubbles to be more asymmetric about the GC.
This is because the denser/faster jets are more likely to\
break through the thin disk in a short time, so that\
the jets have insufficient time to interact with the disk to change their orientations and then be vertically elongated by the stratified atmosphere.

Finally, we find that increasing the source temperature (B$\rightarrow$C$\rightarrow$D)\
not only improves the symmetry of the bubbles but also increases the temperature
inside the bubbles at the present time. This result implies that a high-temperature source
helps the jets ablate the clumpy dense gas away and pours into the atmosphere
through the intercloud channels of the clumpy disk. In contrast,
if source temperature is not high enough,
the jets cannot effectively ablate the high-density clouds within 12.39 Myr,
resulting in the formation of asymmetric bubbles (case B).
